---
title: "Interactive Profile"
resource_files:
- myphoto.jpeg
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    source_code: https://github.com/YspAnimal/Interactive-CV
    theme: spacelab
---

```{r setup, include=FALSE}
library(flexdashboard)
library(data.table)
library(ggplot2)
library(dplyr)
library(purrr)
library(timevis)
library(lubridate)
library(openxlsx)
library(shiny.semantic)
timeLineData <- read.xlsx("./WorkingPath.xlsx", sheet = 1, detectDates = TRUE)
timeLineData$content <- timeLineData$place
projects <- read.xlsx("./WorkingPath.xlsx", sheet = 2)
skills <- read.xlsx("./WorkingPath.xlsx", sheet = 3)
timeLineCourses <- read.xlsx("./WorkingPath.xlsx", sheet = 4, detectDates = TRUE)
timeLineCourses$content <- timeLineCourses$Course
cssButtonStyle <- "margin-bottom:4px; border-radius: 12px;background-color: white; color: gray"


```

Column {.sidebar}
======================
```{r}
HTML("
<br>
<center>
    <img src=\"myphoto.jpeg\" alt=\"Avatar\" style=\"width:200px; border-radius:50%\">
</center>
<br>
")
HTML('<hr style="color: gray;">')
```

##Details

**Name:**
Nikolay Solovey

**Age:**
32 years

**Location:**
Izhevsk, Russia. Open to the world)

**Education:**
BS Mathematics
Specialist Applied Math

```{r}
HTML('<hr style="color: gray;">')
```

About {data-icon="fa-user"}
======================

System Engineer / IT Manager

Hi Everyone!

I`m senior system engineer with a good knowledge of mathematics, statistics and process management. After 10 years in IT(Servers, Virtualization, Video conferencing solutions, ERP systems, ITSM), I've decided to transit into data analytics, data mining and machine learning fields. Please follow to the "Careers" and the "Education & Training" sections for exploring my working experience, career, projects list and education.


This is my first open project in "Web" and "Analytics" cases that uses R+Shiny for sharing my past and current experience for everybody! Future plans: As the next step app will use a more flexible approaches, such as using API of the biggest Russian HR portal hh.ru and scrapping data from my personal CV in automatic mode.






Careers {data-icon="fa-building"}
======================

### Working Path
```{r}
fluidRow(
    column(width = 8,
      timevisOutput('timeLineWork'),
      wellPanel(
        div(id="skillsButtons")
      )
    ),
    column(width = 4,
      DT::dataTableOutput("projects")       
    )
  )
  fluidRow(
    column(width = 8,
           titlePanel("Work overview")
           ),
    column(width = 4,
           titlePanel("Project description")
           
           )
    
  )
output$timeLineWork <- renderTimevis({
  timevis(timeLineData, showZoom = FALSE, height = 250)
  })

inserted <- c()

observeEvent(input$timeLineWork_selected, {
  ## Filtering data based on timeLine select
  selectedCompany <- timeLineData %>% 
    filter(id == as.numeric(input$timeLineWork_selected)) %>% 
    select(place)
  selectedSkills <- skills %>% 
    filter(company %in% selectedCompany)
  ## Clear earlier inserted buttons
  if (!is.null(inserted)) {
    map(inserted, function(x){
      removeUI(selector =  paste0("#", x))
    })
  }
  
  ## Create buttons list for inserting
  idNum <- 1
  skillsButtons <- map(selectedSkills$keySkills, function(x){
    id <- paste0('skill', idNum)
    inserted[idNum] <<- id
    button <- actionButton(id, x, style = cssButtonStyle)
    idNum <<- idNum + 1
    return(button)
  })
  insertUI(
    selector = "#skillsButtons", 
    ui = skillsButtons
  )
  
  output$projects <- DT::renderDataTable({
    projects %>% filter(company %in% selectedCompany) %>% select(project, status)
  }, selection = 'single', options = list(dom = 't'))
  
})

```

Education & Training {data-icon="fa-graduation-cap"}
======================
###Learning Path

```{r}
#fluidPage(
  fluidRow(
    column(width = 12,
      timevisOutput('timeLineCourses'),
      wellPanel(
        div(id="certificate")
      )
    )
  )
#)
output$timeLineCourses <- renderTimevis({
  timevis(timeLineCourses, showZoom = FALSE, height = 250)
  })

observeEvent(input$timeLineCourses_selected, {
  selectedCourse <- timeLineCourses %>% 
    filter(id == as.numeric(input$timeLineCourses_selected))
  
  insertUI(
    selector = "#certificate", 
    ui = tags$iframe(src = selectedCourse$Certificate, seamless=NA)
  )

})
```


